---
title: "QUALITY CONTROL"
author: "Bac Tran"
date: '2022-06-08'
output: html_document
---

##Environment

First we shall load the necessary packages
```{r}
library(lubridate)
library(dplyr)
library(qicharts2)
```
##Data

We load the data by reading "monitor.csv" file. The csv file need to be in the same directory as this notebook.
The data has 10,000 observations and 4 variable. 
We need to turn Timpestamp column to Date data type.
We add more column day of year for chart plotting task.

```{r}
dat <- read.csv("monitor.csv", header = TRUE)
dat$Timestamp <- as.Date(dat$Timestamp) #Turn Timestamp to Date data type
dat$day_of_year <- yday(dat$Timestamp) # add the column day of year
str(dat)
```

##Group by day of year

Now we group the data by day of year.
```{r}
# Define group per day of year
group <- dat %>% group_by(day_of_year)
group
```
We will use control charts such as "Xbar" and "S" to show the model is in or out of control in term of memory usage, prediction time, predictions.
The XBAR chart plots the means of the sets of consecutive points. An XBAR chart shows whether the process mean is in control.
The S chart plots the standard deviation of the sets of consecutive points. An S chart shows whether the process variability is in control.

We assume the first 40 days of data can be used to establish the control limits for the remainder of the data.

##PROCESS MEMORY

#Xbar-chart for memory usage of server

```{r}
data_memory <- group[, c(2,5)] #Process Memory grouped by day of year
XBAR_ProcessMemory <- qicharts2::qic(x = data_memory$day_of_year, y = data_memory$ProcessMemory, data = data_memory, chart = "xbar", freeze = 40, title = "XBAR Chart of Process Memory")
plot(XBAR_ProcessMemory)
```

```{r}
summary(XBAR_ProcessMemory)
```

#S-chart for memory usage of server
Let’s take a look at the variability of memory usage of server by ploting S chart.

```{r}
# Plot S-chart for ProcessMemory variable
S_ProcessMemory <- qicharts2::qic(x = data_memory$day_of_year, y = data_memory$ProcessMemory, data = data_memory, chart = "s", freeze = 40, title = "S Chart of Process Memory")
plot(S_ProcessMemory)
```

```{r}
summary(S_ProcessMemory)
```

##PREDICTION

#Xbar-chart for Prediction
```{r}
data_predict <- group[, c(3,5)] # Prediction grouped by day of year

XBAR_Prediction <- qicharts2::qic(x = data_predict$day_of_year, y = data_predict$Prediction, data = data_predict, chart = "xbar", freeze = 40, title = "XBAR Chart of Prediction")
plot(XBAR_Prediction)
```

```{r}
summary(XBAR_Prediction)
```

#S-chart for Prediction

```{r}
S_Prediction <- qicharts2::qic(x = data_predict$day_of_year, y = data_predict$Prediction, data = data_predict, chart = "s", freeze = 40, title = "S Chart of Prediction")
plot(S_Prediction)
```

```{r}
summary(S_Prediction)
```

##PREDICTION TIME

#Xbar-chart for Prediction Time
```{r}
data_predict_time <- group[, c(4,5)] #Prediction Time grouped by day of year

XBAR_Predic_time <- qicharts2::qic(x = data_predict_time$day_of_year, y = data_predict_time$PredictionTimeMS, data = data_predict_time, chart = "xbar", freeze = 40, title = "XBAR Chart of Prediction Time ms")
plot(XBAR_Predic_time)
```

```{r}
summary(XBAR_Predic_time)
```

#S-chart for Prediction Time

```{r}
S_Predic_time <- qicharts2::qic(x = data_predict_time$day_of_year, y = data_predict_time$PredictionTimeMS, data = data_predict_time, chart = "s", freeze = 40, title = "S Chart of Prediction Time ms")
plot(S_Predic_time)
```

```{r}
summary(S_Predic_time)
```

##QUALITY CONTROL TABLE

```{r}
#Turn summary result to data frame
X_m <- as.data.frame(summary(XBAR_ProcessMemory))
X_p <- as.data.frame(summary(XBAR_Prediction))
X_t <- as.data.frame(summary(XBAR_Predic_time))
S_m <- as.data.frame(summary(S_ProcessMemory))
S_p <- as.data.frame(summary(S_Prediction))
S_t <- as.data.frame(summary(S_Predic_time))

#get the sigma.signal and run.signal from summary data
x_breach <- c(X_m$sigma.signal,X_p$sigma.signal, X_t$sigma.signal)
x_run_signal <- c(X_m$runs.signal,X_p$runs.signal, X_t$runs.signal)
s_breach <- c(S_m$sigma.signal,S_p$sigma.signal, S_t$sigma.signal)
s_run_signal <- c(S_m$runs.signal,S_p$runs.signal, S_t$runs.signal)

#create quality control data frame
qc <- data.frame(Mesurement = c("Memory","Prediction","Time"),
                Xbar_breaches = x_breach,
                Xbar_runs_signal = x_run_signal,
                S_breaches = s_breach,
                S_runs_signal = s_run_signal)

#Create the Overall column based on values of run signal of Xbar and S. If all values xbar and s of the measurement equal 0, it is considered In Control. Otherwise it's Out of Control.
qc <- qc %>% mutate(Overall = if_else(Xbar_runs_signal == 0 & Xbar_breaches == 0
                                     &   S_runs_signal == 0 & S_runs_signal == 0,
                                     "In Control", "Out of Control"))

qc

```

We can see all 3 Measurements are Out of Control.


